%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Titouan}{Bion}
\address{13 avenue Jean Moulin,\\
\hspace*{\fill}40000 Mont-de-Marsan\\
\hspace*{\fill}France} % FIXME: use template instead of hfill here !
\mobile{(+33) 6 32 12 59 25}
\email{titouan.bion@gmail.com}

\recipient{Epidemic Sound}{Åsögatan 121\\
116 24 Stockholm\\
Sweden}

% Defines the title for letter (cover letter only, optional)
\lettertitle{Object: Full Stack Developer}

% Defines the date for letter (cover letter only)
\letterdate{\today}

% Defines a message of opening for letter (cover letter only)
\letteropening{
Dear Sir or Madam,
\medskip
}

% Defines a message of closing for letter (cover letter only)
\letterclosing{
Yours faithfully,
\medskip
}

% Defines an enclosure for letter (cover letter only, optional)
%\letterenclosure[<enclosure name>]{<enclosure>}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
{\today}
{Titouan Bion~~~·~~~Cover letter}
{\thepage}

\begin{document}
  %%% Make a header for CV with personal data
  %\makecvheader

  % Define a title of the cover letter
  \makelettertitle

  \begin{cvletter}
    I am a Software Development Engineer, currently working within the Service Départemental d’Incendie et de Secours du 64 --- SDIS64 ---,
    a fire brigade and call centre supervising 7600km\textsuperscript{2} of the French territory.
    I passed a two-year scientific curriculum before entering the École Internationale des Sciences du Traitement de l’Information ---
    a French Engineering School in Computer Science ---, where I graduated and received
    a Master's Degree in Computer Science with a focus on distributed architecture and Cloud infrastructure.
    Throughout my studies, I gained rigour, methods and purpose:
    I am not overwhelmed when facing a great amount of work but eager to devote time to learning in order to further put my knowledge into practice.
    \medskip

    Not only am I passionate about software engineering, but I am also a fervent music listener and producer, hence my heartfelt interest for Epidemic Sound.
    Committed to continuously developing my Computer Science skills together with enhancing my musical enthusiasm,
    I am highly motivated to work as a Full Stack Developer within the company.
    Indeed, it would be a great source of fulfilment to contribute to services using cutting-edge technologies to improve music distribution.
    \medskip

    My work at Ippon Technologies on building distributed backend systems could be valuable to handle large architectures,
    thus helping your transition towards "a more self-serving and data-driven platform".
    Within a team of four engineers, I implemented micro services meant to be used by hundreds of salesmen through an Android application.
    Furthermore, we developed an asynchronous pipeline to address the customers information storage consistency issue
    and to optimise time-consuming checkout.
    Through this experience, I also became familiar with continuous deployment and automated testing.
    It hence allowed me to build a complete continuous deployment and continuous integration environment for the fire station IT department.

    As for the frontend part, my mission within the SDIS64 includes design and implementation of Angular2 user interfaces
    which aggregate data from multiple sources.
    These data are updated in real-time and displayed 24/7 to call centre operators on an operational wall to help decision making
    and anticipation during emergency services' interventions.
    \medskip

    I would learn from working at Epidemic Sound, in an innovative environment, where everything revolves around music.
    Moreover, it would be thrilling to overcome the challenge of building for high availability, low latency and scalability.
    \medskip

    Acquainted with Sweden and particularly attached to Stockholm, I would make the most of my position at Epidemic Sound to enjoy both the Swedish culture
    and the dynamic work environment to provide better performances.
    \medskip

    I thank you, Sir, Madam, for your time and consideration.
    I can make myself available at any time to plan an interview or to provide you with more information.
  \end{cvletter}

  % Define a closing of the cover letter
  \makeletterclosing
\end{document}
