\cvsection{Experience}
\begin{cventries}
  \cventry
  {SRE - Software Developper}
  {OVHcloud}
  {Toulouse, France}
  {Jun. 2022 - Now}
  {
  \begin{cvitems}
  	\item {Working in team that maintains public cloud infrastructure using OpenStack over 20 000 hosts for more than 1 000 000 cores spread in 8 countries.}
	\item {Python programming to help self-healing or optimize control plane host placement spread in datacenters.}
	\item {Became OpenStack Mistral project team lead and contributor to maintain project as it's core to our self-healing strategy.}
	\item {Done operation for maintenance of the infrastructure as well as on-call duty.}
    \item {Technologies : Python, OpenStack, Ansible, Puppet, Grafana, Prometheus}
  \end{cvitems}
  }
  \cventry
  {Security Analyst}
  {NBS System}
  {Nantes, France (working from home)}
  {Jan. 2021 - May 2022}
  {
  \begin{cvitems}
    \item {Maintaining high security level for over 5000 machines, hosting from eshop website to full enterprise information system, with infrastructure and application review.}
    \item {Maintaining and upgrading an internally developped SIEM to help with the global security, as well as the open source WAF NAXSI to help protect web applications}
    \item {Done 2 web forensics analysis for our client after they had a breach (one payment skimmer and one gitlab data loss)}
    \item {Done a full Fortigate firewall configuration review containing over 130 rules}
    \item {Technologies : Golang, Kubernetes, Terraform, AWS, ElasticSearch, Grafana, Kafka, NGINX, NAXSI}
  \end{cvitems}
  }
  \cventry
  {C++ Teacher}
  {Ecole Internationale des Science du Traitement de l'Information (EISTI)}
  {Pau, France}
  {Feb. 2017 - May 2017}
  {
  \begin{cvitems}
    \item {Taught C++ basics to a 30 students class in computer science engineering school}
  \end{cvitems}
  }
  \cventry
  {Security system Engineer}
  {Viveris Technologies for Airbus Defence \& Space}
  {Toulouse, France}
  {Sept. 2015 - Sept. 2020}
  {
  \begin{cvitems}
    \item {Development of a test bench for national file gateway using FTP/SFTP to automate and accelerate testing. Integrated in Jenkins for CI.}
    \item {Automating installation for unidirectionnal file gateway, to make it easily installable and configurable by technicians.}
    \item {Exportable file gateway system development and automation with low level container for security.}
    \item {System hardening for exportable file gateway with OpenSCAP to enforce security at installation.}
    \item {Adapting national file gateway to be run in virtual machines, with virtualization of hardware modules.}
    \item {Software integration in Terraform like proprietary software for deployment on 3 redundant worker nodes and 2 redundant database nodes.}
    \item {Technologies : Python, Bash, RedHat/CentOS RPM, LXC, OpenSCAP, SoftHSM, PostgreSQL, Heartbeat/Pacemake, DRBD}
  \end{cvitems}
  }
%  \cventry
%  {Viveris Technologies}
%  {Internship}
%  {Toulouse, France}
%  {Apr. 14 - Aug. 2014}
%  {
%  \begin{cvitems}
%    \item {Installation of a private cloud, directly operated by developpers.}
%    \item {Used for the development and production of around 10 projects on 2 worker nodes}
%    \item {Technologies: Openstack Juno (Nova, Neutron, Swift, Horizon), Debian 7}
%  \end{cvitems}
%  }
  %\cventry
  %{Data Engineer <Intern>}
  %{Ippon Technologies}
  %{Bordeaux Area, France}
  %{May 2017 - Oct. 2017}
  %{
  %\begin{cvitems}
  %  \item {Micro-services development to scale and optimise Cultura's backend --- a large French retail chain selling cultural and electronic products --- improving working conditions and productivity of hundreds of Cultura's sales consultants.}
  %  \item {Technologies: JavaEE (Spring), Docker, Gradle, Angular2/4, ElasticSearch, RabbitMQ, Go}
  %\end{cvitems}
  %}
  %\cventry
  %{Software Development Engineer <Intern>}
  %{Technische Universität Dresden}
  %{Dresden, Germany}
  %{Jun. 2016 - Oct. 2016}
  %{
  %\begin{cvitems}
  %  \item {Development of a new Yahoo! Cloud Serving Benchmark software module allowing chart visualisation of benchmarks results on a web interface updated in real time during the benchmark run.}
  %  \item {Technologies: AngularJS, NodeJS, NoSQL (MongoDB), Java8}
  %\end{cvitems}
  %}
\end{cventries}
